Ecudor plant species IUCN statuses

### 2022-09-26 code/L0/L0_Ecuador_plants_IUCN.Rmd
Rename L0_2_Ecuador_plants_IUCN.Rmd to L0_Ecuador_plants_IUCN.Rmd

# Install and load required packages
```{r}
for (package in c("httr", "jsonlite", "rredlist", "dplyr")) {
  if (!require(package, character.only=T, quietly=T)) {
    install.packages(package)
    library(package, character.only=T)
  }
}
```
# Set up token and api url
```{r}
## Token for accessing IUCN data through their API
## User must obtain a token (https://apiv3.iucnredlist.org/api/v3/token) before using the 'rredlist package'.
token <- 'f632af67ee5eef8446a8cb0ca394e1f1cb369ca5eab626edc4ea46e5698deb25'
api_url <- 'https://apiv3.iucnredlist.org/api/v3/'

@@

# Generate Ecuador plant list
```{r}
ecuador_plants <- merge(all_plants, ecuador_species, by="taxonid")
ecuador_plants_unique <- distinct(ecuador_plants, scientific_name, .keep_all = TRUE)
```

# Summary of data
```{r}
#need better summary info
summary(ecuador_plants)
```

# Write data to csv
```{r}
ecuador_plants_ICUN <- file.path(output_path,"ecuador_plants_IUCN.csv")
write.csv(ecuador_plants, ecuador_plants_ICUN)
```

```{r}
all_habitat_plants <- ecuador_plants %>%
  rowwise %>%
  do(rl_habitats(.$taxonid))
```

>>>>

# Install and load required packages
```{r}
for (package in c("httr", "jsonlite", "rredlist", "dplyr", "mde")) {
  if (!require(package, character.only=T, quietly=T)) {
    install.packages(package)
    library(package, character.only=T)
  }
}
```
# Set up token and api url
```{r}
## Token for accessing IUCN data through their API
## User must obtain a token (https://apiv3.iucnredlist.org/api/v3/token) before using the 'rredlist package'.
token <- 'f632af67ee5eef8446a8cb0ca394e1f1cb369ca5eab626edc4ea46e5698deb25'
api_url <- 'https://apiv3.iucnredlist.org/api/v3/'

@@

# Generate Ecuador plant species list
```{r}
ecuador_plants <- merge(all_plants, ecuador_species, by="taxonid")
```

# Get occurences for Ecuador using species list
```{r}
get_occ <- function(ID) {
  rl_occ_country<- rl_occ_country(id=ID,key=token)$result
  if (class(rl_occ_country) == 'data.frame') {
    data.frame(taxonid=ID, rl_occ_country)
  } else {
    data.frame(taxonid=ID)
  }
}
ecuador_IUCN_plant_occ <- ecuador_plants %>%
  rowwise %>%
  do(get_occ(.$taxonid))
ecuador_IUCN_plant_occ <- as.data.frame(ecuador_IUCN_plant_occ)
```

# Get habitat for species list
```{r}
get_habitat <- function(ID) {
  habitat_by_sp<- rl_habitats(id=ID,key=token)$result
  if (class(habitat_by_sp) == 'data.frame') {
    data.frame(taxonid=ID, habitat_by_sp)
  } else {
    data.frame(taxonid=ID)
  }
}
ecuador_IUCN_plant_habitat <- ecuador_plants %>%
  rowwise %>%
  do(get_habitat(.$taxonid))
ecuador_IUCN_plant_habitat <- as.data.frame(ecuador_IUCN_plant_habitat)
```

# Summary of data
```{r}
summary(ecuador_plants)
na_summary(ecuador_plants, exclude_cols = c("subpopulation"))
```

```{r}
summary(ecuador_IUCN_plant_occ)
na_summary(ecuador_IUCN_plant_occ)
```

```{r}
summary(ecuador_IUCN_plant_habitat)
na_summary(ecuador_IUCN_plant_habitat)
```

# Write data to csv
```{r}
ecuador_ICUN_species_list_path <- file.path(output_path,"Ecuador_IUCN_plant_species.csv")
write.csv(ecuador_plants, file = ecuador_ICUN_species_list_path)

ecuador_IUCN_plant_occ_path <- file.path(output_path, "Ecuador_IUCN_plant_occ.csv")
write.csv(ecuador_IUCN_plant_occ, file = ecuador_IUCN_plant_occ_path)

ecuador_IUCN_plant_habitat_path <- file.path(output_path, "Ecuador_IUCN_plant_habitat.csv")
write.csv(ecuador_IUCN_plant_habitat, file = ecuador_IUCN_plant_habitat_path)
```
